Stability of Dynamical System Ensembles

### 2014-09-09 journal.tex
comment out support information
fix typo

%    Information for first author
\author{Aviv Bergman}
%    Address of record for the research reported here
\address{Department of Systems and Computational Biology, Albert Einstein College of Medicine, Bronx, New York 10461}
%    Current address
\curraddr{}
\email{aviv@einstein.yu.edu}
%    \thanks will become a 1st page footnote.
\thanks{The first author was supported in part by NSF Grant \#000000.}

%    Information for second author
\author{Raymond S. Puzio}
\address{Department of Systems and Computational Biology, Albert Einstein College of Medicine, Bronx, New York 10461}
%    Current address
\curraddr{}
\email{rsp@novres.org}
\thanks{Support information for the second author.}

%    Information for third author
\author{Cameron Smith}
\address{Department of Systems and Computational Biology, Albert Einstein College of Medicine, Bronx, New York 10461}
%    Current address
\curraddr{}
\email{cameron.smith@med.einstein.yu.edu}
\thanks{Support information for the second author.}

%    General info
\subjclass[2000]{Primary 54C40, 14E20; Secondary 46E25, 20C20}

\date{January 1, 2001 and, in revised form, June 22, 2001.}

\dedicatory{This paper is dedicated to our advisors.}

\keywords{Differential geometry, algebraic geometry}

@@

Introduce $V$ as the parameter space of all polynomials or degree $n$
with real coefficients.  In other words, $V$ is a real vector space of
dimension $n$ whose coordinates we will identify with the coefficients
$s_k$ of our polynomial.  We now partition this space into regions
corresponding to specific types of polynomials.  Let $R_{abcd}$ be the
subset of $V$ such that $x \in R_{abcd}$ iff the polynomial
corresponding to $x$ has $a$ positive real roots, $b$ negative real
roots, $c$ complex roots with positive real part and $d$ complex roots
with negative real part.  Once we characterize these regions using
invariants, we will have solved the original problem because a matrix
is stable if the point of $V$ corresponding to it lies in a region of
the form $R_{a0c0}$.

>>>>

%    Information for first author
\author{Aviv Bergman}
%    Address of record for the research reported here
\address{Department of Systems and Computational Biology, Albert Einstein College of Medicine, Bronx, New York 10461}
%    Current address
\curraddr{}
\email{aviv@einstein.yu.edu}
%    \thanks will become a 1st page footnote.
% \thanks{The first author was supported in part by NSF Grant \#000000.}

%    Information for second author
\author{Raymond S. Puzio}
\address{Department of Systems and Computational Biology, Albert Einstein College of Medicine, Bronx, New York 10461}
%    Current address
\curraddr{}
\email{rsp@novres.org}
% \thanks{Support information for the second author.}

%    Information for third author
\author{Cameron Smith}
\address{Department of Systems and Computational Biology, Albert Einstein College of Medicine, Bronx, New York 10461}
%    Current address
\curraddr{}
\email{cameron.smith@med.einstein.yu.edu}
% \thanks{Support information for the second author.}

%    General info
% \subjclass[2000]{Primary 54C40, 14E20; Secondary 46E25, 20C20}

% \date{January 1, 2001 and, in revised form, June 22, 2001.}

% \dedicatory{This paper is dedicated to our advisors.}

% \keywords{Differential geometry, algebraic geometry}

@@

Introduce $V$ as the parameter space of all polynomials of degree $n$
with real coefficients.  In other words, $V$ is a real vector space of
dimension $n$ whose coordinates we will identify with the coefficients
$s_k$ of our polynomial.  We now partition this space into regions
corresponding to specific types of polynomials.  Let $R_{abcd}$ be the
subset of $V$ such that $x \in R_{abcd}$ iff the polynomial
corresponding to $x$ has $a$ positive real roots, $b$ negative real
roots, $c$ complex roots with positive real part and $d$ complex roots
with negative real part.  Once we characterize these regions using
invariants, we will have solved the original problem because a matrix
is stable if the point of $V$ corresponding to it lies in a region of
the form $R_{a0c0}$.
